---
title: "statistical_learning"
author: "Cintia Anna Nagy"
date: "`r Sys.Date()`"
output: html_document
---

# import packages

```{r message = FALSE}
library(tidyverse)
library(rstatix)
library(readr)
library(dplyr)
library(car)
library(tidyverse)
library(sjPlot)
library(lme4)
library(performance)
library(nortest)
library(lmeresampler)
```

# import data

```{r message = FALSE}
study1_stat_learn <- read_csv("processed_data/study_1/data_study_1_statistical_learning.csv")
study1_visuomotor_perf  <- read_csv("processed_data/study_1/data_study_1_visuomotor_performance.csv")
study2_stat_learn  <- read_csv("processed_data/study_2/data_study_2_statistical_learning.csv")
study2_visuomotor_perf  <- read_csv("processed_data/study_2/data_study_2_visuomotor_performance.csv")
```

# preprocess data
## Study 1 (AQ)

```{r}
study1_stat_learn_long <- study1_stat_learn %>% 
  select(c('AQ_total', 'Subject', 'e1_H','e2_H','e3_H','e4_H','e5_H', 'e1_L','e2_L','e3_L','e4_L','e5_L'))

blocks <- c('e1','e2','e3','e4','e5')

study1_stat_learn_long <- pivot_longer(
  data = study1_stat_learn_long,
  cols = starts_with(blocks),
  names_to = c(".value", "Triplet"),
  names_pattern = "([^_]+)_(\\D+)",
  values_to = "Triplet"
)

study1_stat_learn_long <- pivot_longer(
  data = study1_stat_learn_long,
  cols = starts_with(blocks),
  names_to = c("Blocks"),
  values_to = "stat_learn"
)

study1_stat_learn_long <- study1_stat_learn_long %>% 
  mutate(Block = gsub('e', "", Blocks))

# center block and AQ_total variable
study1_stat_learn_long <- study1_stat_learn_long %>% 
  mutate(Block = as.numeric(Block),
         Block_centered = scale(Block, center = T, scale = F),
         AQ_total_centered = scale(AQ_total, center = T, scale = F))
```

```{r}
study1_visuomotor_perf_long <- study1_visuomotor_perf %>% 
  select(c('AQ_total', 'Subject', 'e1','e2','e3','e4', 'e5'))

blocks <- c('e1','e2','e3','e4', 'e5')

study1_visuomotor_perf_long <- pivot_longer(
  data = study1_visuomotor_perf_long,
  cols = starts_with(blocks),
  names_to = c("Blocks"),
  values_to = "visuomotor_perf"
)

study1_visuomotor_perf_long <- study1_visuomotor_perf_long %>% 
  mutate(Block = gsub('e', "", Blocks))

# center block and AQ_total variable
study1_visuomotor_perf_long <- study1_visuomotor_perf_long %>% 
  mutate(Block = as.numeric(Block),
         Block_centered = scale(Block, center = T, scale = F),
         AQ_total_centered = scale(AQ_total, center = T, scale = F))
```

## Study 2

```{r}
study2_stat_learn_long <- study2_stat_learn %>% 
  select(c('Group', 'Subject', 'e1_H','e2_H','e3_H','e4_H', 'e1_L','e2_L','e3_L','e4_L'))

blocks <- c('e1','e2','e3','e4')

study2_stat_learn_long <- pivot_longer(
  data = study2_stat_learn_long,
  cols = starts_with(blocks),
  names_to = c(".value", "Triplet"),
  names_pattern = "([^_]+)_(\\D+)",
  values_to = "Triplet"
)

study2_stat_learn_long <- pivot_longer(
  data = study2_stat_learn_long,
  cols = starts_with(blocks),
  names_to = c("Blocks"),
  values_to = "stat_learn"
)

study2_stat_learn_long <- study2_stat_learn_long %>% 
  mutate(Block = gsub('e', "", Blocks))
```

```{r}
study2_visuomotor_perf_long <- study2_visuomotor_perf %>% 
  select(c('Group', 'Subject', 'e1','e2','e3','e4'))

blocks <- c('e1','e2','e3','e4')

study2_visuomotor_perf_long <- pivot_longer(
  data = study2_visuomotor_perf_long,
  cols = starts_with(blocks),
  names_to = c("Blocks"),
  values_to = "visuomotor_perf"
)

study2_visuomotor_perf_long <- study2_visuomotor_perf_long %>% 
  mutate(Block = gsub('e', "", Blocks))
```

## Study 1 (AQ)

```{r}
study1_stat_learn_long <- study1_stat_learn %>% 
  select(c('Group', 'Subject', 'e1_H','e2_H','e3_H','e4_H','e5_H', 'e1_L','e2_L','e3_L','e4_L','e5_L'))

blocks <- c('e1','e2','e3','e4','e5')

study1_stat_learn_long <- pivot_longer(
  data = study1_stat_learn_long,
  cols = starts_with(blocks),
  names_to = c(".value", "Triplet"),
  names_pattern = "([^_]+)_(\\D+)",
  values_to = "Triplet"
)

study1_stat_learn_long <- pivot_longer(
  data = study1_stat_learn_long,
  cols = starts_with(blocks),
  names_to = c("Blocks"),
  values_to = "stat_learn"
)

study1_stat_learn_long <- study1_stat_learn_long %>% 
  mutate(Block = gsub('e', "", Blocks))
```

```{r}
study1_visuomotor_perf_long <- study1_visuomotor_perf %>% 
  select(c('Group', 'Subject', 'e1','e2','e3','e4', 'e5'))

blocks <- c('e1','e2','e3','e4', 'e5')

study1_visuomotor_perf_long <- pivot_longer(
  data = study1_visuomotor_perf_long,
  cols = starts_with(blocks),
  names_to = c("Blocks"),
  values_to = "visuomotor_perf"
)

study1_visuomotor_perf_long <- study1_visuomotor_perf_long %>% 
  mutate(Block = gsub('e', "", Blocks))
```

# Study 1 (AQ)
## stat learning: triplet x block x AQ
### baseline model for statistical learning

```{r}
# building model
study1_stat_learn_baseline <-
  lmer(stat_learn ~ Block_centered*Triplet + (1|Subject),
       data = study1_stat_learn_long
       )

# model outputs
summary(study1_stat_learn_baseline)
tab_model(study1_stat_learn_baseline, show.std = T)

# assumption checks
plot_model(study1_stat_learn_baseline, type = "diag")
check_model(study1_stat_learn_baseline)

# visualizing
plot_model(study1_stat_learn_baseline, type = "est")
plot_model(study1_stat_learn_baseline, type = "int")

# goodness of fit indicators
AIC_study1_stat_learn_baseline <- AIC(study1_stat_learn_baseline)
BIC_study1_stat_learn_baseline <- BIC(study1_stat_learn_baseline)

# normality test for residuals
study1_stat_learn_baseline_residuals <- residuals(study1_stat_learn_baseline)
lillie.test(study1_stat_learn_baseline_residuals)

# normality test for learning_score
lillie.test(study1_stat_learn_long$stat_learn)
```

### AQ model for statistical learning

```{r}
# building model
study1_stat_learn_AQ <-
  lmer(stat_learn ~ Block_centered*Triplet*AQ_total_centered + (1|Subject),
       data = study1_stat_learn_long
       )

# model outputs
summary(study1_stat_learn_AQ)
tab_model(study1_stat_learn_AQ, show.std = T)

# assumption checks
plot_model(study1_stat_learn_AQ, type = "diag")
check_model(study1_stat_learn_AQ)

# visualizing
plot_model(study1_stat_learn_AQ, type = "est")
plot_model(study1_stat_learn_AQ, type = "int")

# goodness of fit indicators
AIC_study1_stat_learn_AQ <- AIC(study1_stat_learn_AQ)
BIC_study1_stat_learn_AQ <- BIC(study1_stat_learn_AQ)

# normality test for residuals
study1_stat_learn_AQ_residuals <- residuals(study1_stat_learn_AQ)
lillie.test(study1_stat_learn_AQ_residuals)

# normality test for learning_score
lillie.test(study1_stat_learn_long$stat_learn)
```

### ANOVA test for baseline and AQ model

```{r}
anova(study1_stat_learn_baseline, study1_stat_learn_AQ)
```

### Goodness of fit indicators

```{r}
#AIC
AIC_study1_stat_learn_baseline
AIC_study1_stat_learn_AQ

#BIC
BIC_study1_stat_learn_baseline
BIC_study1_stat_learn_AQ
```

### Bootstrapping

```{r}
baseline_model_boot_residual <- bootstrap(study1_stat_learn_baseline, .f = fixef, B = 1000,  type = "residual", resample = c(TRUE, TRUE))

confint(baseline_model_boot_residual, type = "norm")
```

## visuomotor performance learning: block x AQ
### baseline model for visuomotor performance

```{r}
# building model
study1_visuomotor_perf_baseline <-
  lmer(visuomotor_perf ~ Block_centered + (1|Subject),
       data = study1_visuomotor_perf_long
       )

# model outputs
summary(study1_visuomotor_perf_baseline)
tab_model(study1_visuomotor_perf_baseline, show.std = T)

# assumption checks
plot_model(study1_visuomotor_perf_baseline, type = "diag")
check_model(study1_visuomotor_perf_baseline)

# visualizing
plot_model(study1_visuomotor_perf_baseline, type = "est")

# goodness of fit indicators
AIC_study1_visuomotor_perf_baseline <- AIC(study1_visuomotor_perf_baseline)
BIC_study1_visuomotor_perf_baseline <- BIC(study1_visuomotor_perf_baseline)

# normality test for residuals
study1_visuomotor_perf_baseline_residuals <- residuals(study1_visuomotor_perf_baseline)
lillie.test(study1_visuomotor_perf_baseline_residuals)

# normality test for learning_score
lillie.test(study1_visuomotor_perf_long$visuomotor_perf)
```

### AQ model for visuomotor performance

```{r}
# building model
study1_visuomotor_perf_AQ <-
  lmer(visuomotor_perf ~ Block_centered*AQ_total_centered + (1|Subject),
       data = study1_visuomotor_perf_long
       )

# model outputs
summary(study1_visuomotor_perf_AQ)
tab_model(study1_visuomotor_perf_AQ, show.std = T)

# assumption checks
plot_model(study1_visuomotor_perf_AQ, type = "diag")
check_model(study1_visuomotor_perf_AQ)

# visualizing
plot_model(study1_visuomotor_perf_AQ)

# goodness of fit indicators
AIC_study1_visuomotor_perf_AQ <- AIC(study1_visuomotor_perf_AQ)
BIC_study1_visuomotor_perf_AQ <- BIC(study1_visuomotor_perf_AQ)

# normality test for residuals
study1_visuomotor_perf_AQ_residuals <- residuals(study1_visuomotor_perf_AQ)
lillie.test(study1_visuomotor_perf_AQ_residuals)

# normality test for learning_score
lillie.test(study1_visuomotor_perf_long$visuomotor_perf)
```

### ANOVA test for baseline and AQ model

```{r}
anova(study1_visuomotor_perf_baseline, study1_visuomotor_perf_AQ)
```

 ### Bootstrapping

```{r}
baseline_model_boot_residual <- bootstrap(study1_visuomotor_perf_baseline, .f = fixef, B = 1000,  type = "residual", resample = c(TRUE, TRUE))

confint(baseline_model_boot_residual, type = "norm")
```

### Goodness of fit indicators

```{r}
#AIC
AIC_study1_visuomotor_perf_baseline
AIC_study1_visuomotor_perf_AQ

#BIC
BIC_study1_visuomotor_perf_baseline
BIC_study1_visuomotor_perf_AQ
```

# Study 2
## stat learning: triplet x block x group

```{r}
study2_stat_learn_anova <- anova_test(data = study2_stat_learn_long, wid = "Subject", dv = "stat_learn", between = "Group", within = c("Triplet", "Block"), effect.size = "pes")
study2_stat_learn_anova
```

```{r}
# greenhouse-geisser correction
get_anova_table(study2_stat_learn_anova, correction = c("GG"))
```

## visuomotor performance: block x group

```{r}
study2_visuomotor_perf_anova <- anova_test(data = study2_visuomotor_perf_long, wid = "Subject", dv = "visuomotor_perf", between = "Group", within = c("Block"), effect.size = "pes")
study2_visuomotor_perf_anova
```

```{r}
# greenhouse-geisser correction
get_anova_table(study2_visuomotor_perf_anova, correction = c("GG"))
```

# Study 1 (group)
## stat learning: triplet x block x group

```{r}
study1_stat_learn_anova <- anova_test(data = study1_stat_learn_long, wid = "Subject", dv = "stat_learn", between = "Group", within = c("Triplet", "Block"), effect.size = "pes")
study1_stat_learn_anova
```

```{r}
# greenhouse-geisser correction
get_anova_table(study1_stat_learn_anova, correction = c("GG"))
```

## visuomotor performance: block x group

```{r}
study1_visuomotor_perf_anova <- anova_test(data = study1_visuomotor_perf_long, wid = "Subject", dv = "visuomotor_perf", between = "Group", within = c("Block"), effect.size = "pes")
study1_visuomotor_perf_anova
```

```{r}
# greenhouse-geisser correction
get_anova_table(study1_visuomotor_perf_anova, correction = c("GG"))
```
