---
title: "offline anova"
author: "Cintia Anna Nagy"
date: "`r Sys.Date()`"
output: html_document
---

# import packages

```{r message = FALSE}
library(tidyverse)
library(rstatix)
library(readr)
library(dplyr)
library(car)
library(tidyverse)
library(sjPlot)
library(lme4)
library(performance)
library(nortest)
library(blme)
library(lmeresampler)
```

# import data

```{r message = FALSE}
study1_SL <- read_csv("processed_data/study_1/data_study_1_SL_offline_online.csv")
study1_VP <- read_csv("processed_data/study_1/data_study_1_VP_offline_online.csv")
study2_SL <- read_csv("processed_data/study_2/data_study_2_SL_offline_online.csv")
study2_VP <- read_csv("processed_data/study_2/data_study_2_VP_offline_online.csv")
```

# preprocess data
## Study 1

```{r}
# make long dataset
study1_SL_long <- study1_SL %>% 
  select(c('Group', 'AQ_total', 'Subject', 'offline_SL'))

learning_phase <- c('offline_SL')

study1_SL_long <- pivot_longer(
  data = study1_SL_long,
  cols = learning_phase,
  names_to = c("Learning_phase"),
  values_to = "SL_score"
)

study1_SL_long <- study1_SL_long %>% 
  mutate(AQ_total_centered = scale(AQ_total, center = T, scale = F))
```

```{r}
# make long dataset
study1_VP_long <- study1_VP %>% 
  select(c('Group', 'AQ_total', 'Subject', 'offline_VP'))

learning_phase <- c('offline_VP')

study1_VP_long <- pivot_longer(
  data = study1_VP_long,
  cols = learning_phase,
  names_to = c("Learning_phase"),
  values_to = "VP_score"
)

study1_VP_long <- study1_VP_long %>% 
  mutate(AQ_total_centered = scale(AQ_total, center = T, scale = F))
```

```{r}
# make long dataset
study1_SL_long_block <- study1_SL %>% 
  select(c('Group', 'AQ_total', 'Subject', 'block2_offline','block3_offline', 'block4_offline','block5_offline', 'block6_offline','block7_offline', 'block8_offline','block9_offline', 'block10_offline',
                                       'block11_offline', 'block12_offline','block13_offline', 'block14_offline','block15_offline', 'block16_offline', 'block17_offline','block18_offline', 'block19_offline','block20_offline', 'block21_offline', 'block22_offline','block23_offline', 'block24_offline','block25_offline'))

blocks <- c('block2','block3', 'block4','block5', 'block6','block7', 'block8','block9', 'block10',
               'block11', 'block12','block13', 'block14','block15', 'block16', 'block17','block18',
               'block19','block20', 'block21', 'block22','block23', 'block24','block25')

study1_SL_long_block <- pivot_longer(
  data = study1_SL_long_block,
  cols = starts_with(blocks),
  names_to = c("Block"),
  values_to = "SL_score"
)

study1_SL_long_block <- study1_SL_long_block %>% 
  mutate(Block = gsub('_offline', "", Block)) %>% 
  mutate(Block = gsub('block', "", Block))

study1_SL_long_block <- study1_SL_long_block %>% 
  mutate(Block = as.numeric(Block),
         Block_centered = scale(Block, center = T, scale = F),
         AQ_total_centered = scale(AQ_total, center = T, scale = F))
```

```{r}
# make long dataset
study1_VP_long_block <- study1_VP %>% 
  select(c('Group', 'AQ_total', 'Subject', 'block2_offline','block3_offline', 'block4_offline','block5_offline', 'block6_offline','block7_offline', 'block8_offline','block9_offline', 'block10_offline',
                                       'block11_offline', 'block12_offline','block13_offline', 'block14_offline','block15_offline', 'block16_offline', 'block17_offline','block18_offline', 'block19_offline','block20_offline', 'block21_offline', 'block22_offline','block23_offline', 'block24_offline','block25_offline'))

blocks <- c('block2','block3', 'block4','block5', 'block6','block7', 'block8','block9', 'block10',
               'block11', 'block12','block13', 'block14','block15', 'block16', 'block17','block18',
               'block19','block20', 'block21', 'block22','block23', 'block24','block25')

study1_VP_long_block <- pivot_longer(
  data = study1_VP_long_block,
  cols = starts_with(blocks),
  names_to = c("Block"),
  values_to = "VP_score"
)

study1_VP_long_block <- study1_VP_long_block %>% 
  mutate(Block = gsub('_offline', "", Block)) %>% 
  mutate(Block = gsub('block', "", Block))

study1_VP_long_block <- study1_VP_long_block %>% 
  mutate(Block = as.numeric(Block),
         Block_centered = scale(Block, center = T, scale = F),
         AQ_total_centered = scale(AQ_total, center = T, scale = F))
```

## Study 2

```{r}
# make long dataset
study2_SL_long <- study2_SL %>% 
  select(c('Group', 'Subject', 'offline_SL'))

learning_phase <- c('offline_SL')

study2_SL_long <- pivot_longer(
  data = study2_SL_long,
  cols = learning_phase,
  names_to = c("Learning_phase"),
  values_to = "SL_score"
)
```

```{r}
# make long dataset
study2_VP_long <- study2_VP %>% 
  select(c('Group', 'Subject', 'offline_VP'))

learning_phase <- c('offline_VP')

study2_VP_long <- pivot_longer(
  data = study2_VP_long,
  cols = learning_phase,
  names_to = c("Learning_phase"),
  values_to = "VP_score"
)
```

```{r}
# make long dataset
study2_SL_long_block <- study2_SL %>% 
  select(c('Group', 'Subject', 'block2_offline','block3_offline', 'block4_offline','block5_offline', 'block6_offline','block7_offline', 'block8_offline','block9_offline', 'block10_offline',
                                       'block11_offline', 'block12_offline','block13_offline', 'block14_offline','block15_offline', 'block16_offline', 'block17_offline','block18_offline', 'block19_offline','block20_offline'))

blocks <- c('block2','block3', 'block4','block5', 'block6','block7', 'block8','block9', 'block10',
               'block11', 'block12','block13', 'block14','block15', 'block16', 'block17','block18',
               'block19','block20')

study2_SL_long_block <- pivot_longer(
  data = study2_SL_long_block,
  cols = starts_with(blocks),
  names_to = c("Block"),
  values_to = "SL_score"
)

study2_SL_long_block <- study2_SL_long_block %>% 
    mutate(Block = gsub('_offline', "", Block)) %>% 
    mutate(Block = gsub('block', "", Block))
```

```{r}
# make long dataset
study2_VP_long_block <- study2_VP %>% 
  select(c('Group', 'Subject', 'block2_offline','block3_offline', 'block4_offline','block5_offline', 'block6_offline','block7_offline', 'block8_offline','block9_offline', 'block10_offline',
                                       'block11_offline', 'block12_offline','block13_offline', 'block14_offline','block15_offline', 'block16_offline', 'block17_offline','block18_offline', 'block19_offline','block20_offline'))

blocks <- c('block2','block3', 'block4','block5', 'block6','block7', 'block8','block9', 'block10',
               'block11', 'block12','block13', 'block14','block15', 'block16', 'block17','block18',
               'block19','block20')

study2_VP_long_block <- pivot_longer(
  data = study2_VP_long_block,
  cols = starts_with(blocks),
  names_to = c("Block"),
  values_to = "VP_score"
)

study2_VP_long_block <- study2_VP_long_block %>% 
  mutate(Block = gsub('_offline', "", Block)) %>% 
  mutate(Block = gsub('block', "", Block))
```

# Study 1 (AQ)
## Statistical learning
### AQ model for SL

```{r}
# building model
AQ_model_SL <- 
  lm(SL_score ~ AQ_total,
       data = study1_SL_long
       )

# model outputs
summary(AQ_model_SL)
tab_model(AQ_model_SL, show.std = T)

# assumption checks
check_autocorrelation(AQ_model_SL)
check_heteroscedasticity(AQ_model_SL)
check_outliers(AQ_model_SL)
check_model(AQ_model_SL, panel = TRUE)
plot_model(AQ_model_SL, type = "diag")

# visualizing the interactions
plot_model(AQ_model_SL)

# goodness of fit indicators
AIC_AQ_model_SL <- AIC(AQ_model_SL)
BIC_AQ_model_SL <- BIC(AQ_model_SL)

# normality test for residuals
AQ_model_SL_residuals <- residuals(AQ_model_SL)
lillie.test(AQ_model_SL_residuals)

# normality test for learning_score
lillie.test(study1_SL_long$SL_score)
```


### baseline model for SL

```{r}
# building model
baseline_model_SL <- 
  blmer(SL_score ~ Block_centered + (1|Subject),
       data = study1_SL_long_block
       )

# model outputs
summary(baseline_model_SL)
tab_model(baseline_model_SL, show.std = T)

# assumption checks
plot_model(baseline_model_SL, type = "diag")
#check_model(baseline_model_SL)

# visualizing predicted values
plot_model(baseline_model_SL)

# goodness of fit indicators
AIC_baseline_model_SL <- AIC(baseline_model_SL)
BIC_baseline_model_SL <- BIC(baseline_model_SL)

# normality test for residuals
baseline_model_SL_residuals <- residuals(baseline_model_SL)
lillie.test(baseline_model_SL_residuals)

# normality test for learning_score
lillie.test(study1_SL_long_block$SL_score)
```

### AQ model for SL

```{r}
# building model
AQ_model_SL <- 
  blmer(SL_score ~ Block_centered + AQ_total_centered + Block_centered*AQ_total_centered + 
      (1|Subject),
       data = study1_SL_long_block
       )

# model outputs
summary(AQ_model_SL)
tab_model(AQ_model_SL, show.std = T)

# assumption checks
check_collinearity(AQ_model_SL)
plot_model(AQ_model_SL, type = "diag")
#check_model(AQ_model_SL)

# visualizing predicted values
plot_model(AQ_model_SL)

# goodness of fit indicators
AIC_AQ_model_SL <- AIC(AQ_model_SL)
BIC_AQ_model_SL <- BIC(AQ_model_SL)

# normality test for residuals
AQ_model_SL_residuals <- residuals(AQ_model_SL)
lillie.test(AQ_model_SL_residuals)

# normality test for learning_score
lillie.test(study1_SL_long_block$SL_score)
```

### ANOVA test for baseline and AQ model

```{r}
anova(baseline_model_SL, AQ_model_SL)
```

### Goodness of fit indicators

```{r}
#AIC
AIC_baseline_model_SL
AIC_AQ_model_SL

#BIC
BIC_baseline_model_SL
BIC_AQ_model_SL
```

### Bootstrapping

```{r}
baseline_model_boot_residual <- bootstrap(baseline_model_SL, .f = fixef, B = 1000,  type = "residual", resample = c(TRUE, TRUE))

confint(baseline_model_boot_residual, type = "norm")
```


## General skill learning blockwise
### AQ model for VP

```{r}
# building model
AQ_model_VP <- 
  lm(VP_score ~ AQ_total,
       data = study1_VP_long
       )

# model outputs
summary(AQ_model_VP)
tab_model(AQ_model_VP, show.std = T)

# assumption checks
check_autocorrelation(AQ_model_VP)
check_heteroscedasticity(AQ_model_VP)
check_outliers(AQ_model_VP)
check_model(AQ_model_VP, panel = TRUE)
plot_model(AQ_model_VP, type = "diag")

# visualizing the interactions
plot_model(AQ_model_VP)

# goodness of fit indicators
AIC_AQ_model_VP <- AIC(AQ_model_VP)
BIC_AQ_model_VP <- BIC(AQ_model_VP)

# normality test for residuals
AQ_model_VP_residuals <- residuals(AQ_model_VP)
lillie.test(AQ_model_VP_residuals)

# normality test for learning_score
lillie.test(study1_VP_long$VP_score)
```

### baseline model for VP

```{r}
# building model
baseline_model_VP <- 
  lmer(VP_score ~ Block_centered + (1|Subject),
       data = study1_VP_long_block
       )

# model outputs
summary(baseline_model_VP)
tab_model(baseline_model_VP, show.std = T)

# assumption checks
plot_model(baseline_model_VP, type = "diag")
check_model(baseline_model_VP)

# visualizing predicted values
plot_model(baseline_model_VP, type = "est")

# goodness of fit indicators
AIC_baseline_model_VP <- AIC(baseline_model_VP)
BIC_baseline_model_VP <- BIC(baseline_model_VP)

# normality test for residuals
baseline_model_VP_residuals <- residuals(baseline_model_VP)
lillie.test(baseline_model_VP_residuals)

# normality test for learning_score
lillie.test(study1_VP_long_block$VP_score)
```

### AQ model for VP

```{r}
# building model
AQ_model_VP <- 
  lmer(VP_score ~ Block_centered + AQ_total_centered + Block_centered*AQ_total_centered + (1|Subject),
       data = study1_VP_long_block
       )

# model outputs
summary(AQ_model_VP)
tab_model(AQ_model_VP, show.std = T)

# assumption checks
check_collinearity(AQ_model_VP)
plot_model(AQ_model_VP, type = "diag")
check_model(AQ_model_VP)

# visualizing predicted values
plot_model(AQ_model_VP, type = "int")

# goodness of fit indicators
AIC_AQ_model_VP <- AIC(AQ_model_VP)
BIC_AQ_model_VP <- BIC(AQ_model_VP)

# normality test for residuals
AQ_model_VP_residuals <- residuals(AQ_model_VP)
lillie.test(AQ_model_VP_residuals)

# normality test for learning_score
lillie.test(study1_VP_long_block$VP_score)
```

### ANOVA test for baseline and AQ model

```{r}
anova(baseline_model_VP, AQ_model_VP)
```

### Goodness of fit indicators

```{r}
#AIC
AIC_baseline_model_VP
AIC_AQ_model_VP

#BIC
BIC_baseline_model_VP
BIC_AQ_model_VP
```

### Bootstrapping

```{r}
baseline_model_boot_residual <- bootstrap(baseline_model_VP, .f = fixef, B = 1000,  type = "residual", resample = c(TRUE, TRUE))

confint(baseline_model_boot_residual, type = "norm")
```

# Study 2
## statistical learning
### group

```{r}
study2_SL_anova <- anova_test(data = study2_SL_long, wid = "Subject", dv = "SL_score", between = "Group", effect.size = "pes")

get_anova_table(study2_SL_anova)
```

```{r}
# normality test
shapiro_test(study2_SL_long$SL_score)
# homogeneity of variance test
var.test(SL_score ~ Group, data = study2_SL_long)
```

```{r}
# whole offline
mean(study2_SL_long$SL_score)
sd(study2_SL_long$SL_score)

# normality test
shapiro_test(study2_SL_long$SL_score)

# t-test
t.test(study2_SL_long$SL_score)
cohens_d(study2_SL_long, SL_score ~ 1)
```

```{r}
# NTP group offline
NTP_offline <- study2_SL_long %>% 
  filter(Group == 0)
mean(NTP_offline$SL_score)
sd(NTP_offline$SL_score)

# normality test
shapiro_test(NTP_offline$SL_score)

# t-test
t.test(NTP_offline$SL_score)
cohens_d(NTP_offline, SL_score ~ 1)
```

```{r}
# ASD group offline
ASD_offline <- study2_SL_long %>% 
  filter(Group == 1)
mean(ASD_offline$SL_score)
sd(ASD_offline$SL_score)

# normality test
shapiro_test(ASD_offline$SL_score)

# t-test
t.test(ASD_offline$SL_score)
cohens_d(ASD_offline, SL_score ~ 1)
```

### block x group

```{r}
study2_block_SL_anova <- anova_test(data = study2_SL_long_block, wid = "Subject", dv = "SL_score", between = "Group", within = "Block", effect.size = "pes")

# greenhouse-geisser correction
get_anova_table(study2_block_SL_anova, correction = c("GG"))
```

### chi-square test

```{r}
study2_SL_offline_table = table(study2_SL$Group, study2_SL$is_learn_offline)
study2_SL_offline_table
chisq.test(study2_SL_offline_table, correct = FALSE)
```

## visuomotor performance
### group

```{r}
study2_VP_anova <- anova_test(data = study2_VP_long, wid = "Subject", dv = "VP_score", between = "Group", effect.size = "pes")

get_anova_table(study2_VP_anova)
```

```{r}
# normality test
shapiro_test(study2_VP_long$VP_score)
# homogeneity of variance test
var.test(VP_score ~ Group, data = study2_VP_long)
```

```{r}
# whole offline
mean(study2_VP_long$VP_score)
sd(study2_VP_long$VP_score)

# normality test
shapiro_test(study2_VP_long$VP_score)

# t-test
t.test(study2_VP_long$VP_score)
cohens_d(study2_VP_long, VP_score ~ 1)
```

```{r}
# NTP group offline
NTP_offline <- study2_VP_long %>% 
  filter(Group == 0)
mean(NTP_offline$VP_score)
sd(NTP_offline$VP_score)

# normality test
shapiro_test(NTP_offline$VP_score)

# t-test
t.test(NTP_offline$VP_score)
cohens_d(NTP_offline, VP_score ~ 1)
```

```{r}
# ASD group offline
ASD_offline <- study2_VP_long %>% 
  filter(Group == 1)
mean(ASD_offline$VP_score)
sd(ASD_offline$VP_score)

# normality test
shapiro_test(ASD_offline$VP_score)

# t-test
t.test(ASD_offline$VP_score)
cohens_d(ASD_offline, VP_score ~ 1)
```

### block x group

```{r}
study2_block_VP_anova <- anova_test(data = study2_VP_long_block, wid = "Subject", dv = "VP_score", between = "Group", within = "Block", effect.size = "pes")

# greenhouse-geisser correction
get_anova_table(study2_block_VP_anova, correction = c("GG"))
```

### chi-square test

```{r}
study2_VP_offline_table = table(study2_VP$Group, study2_VP$is_learn_offline)
study2_VP_offline_table
chisq.test(study2_VP_offline_table, correct = FALSE)
```


# Study 1 (group)
## statistical learning
### group

```{r}
# normality test
shapiro_test(study1_SL_long$SL_score)
# homogeneity of variance test
var.test(SL_score ~ Group, data = study1_SL_long)
```

```{r}
study1_SL_anova <- anova_test(data = study1_SL_long, wid = "Subject", dv = "SL_score", between = "Group", effect.size = "pes")

get_anova_table(study1_SL_anova)
```

```{r}
# whole offline
mean(study1_SL_long$SL_score)
sd(study1_SL_long$SL_score)

# normality test
shapiro_test(study1_SL_long$SL_score)

# t-test
t.test(study1_SL_long$SL_score)
cohens_d(study1_SL_long, SL_score ~ 1)
```

```{r}
# lowerAQ group offline
lowerAQ_offline <- study1_SL_long %>% 
  filter(Group == 0)
mean(lowerAQ_offline$SL_score)
sd(lowerAQ_offline$SL_score)

# normality test
shapiro_test(lowerAQ_offline$SL_score)

# t-test
t.test(lowerAQ_offline$SL_score)
cohens_d(lowerAQ_offline, SL_score ~ 1)
```

```{r}
# higherAQ group offline
higherAQ_offline <- study1_SL_long %>% 
  filter(Group == 1)
mean(higherAQ_offline$SL_score)
sd(higherAQ_offline$SL_score)

# normality test
shapiro_test(higherAQ_offline$SL_score)

# t-test
t.test(higherAQ_offline$SL_score)
cohens_d(higherAQ_offline, SL_score ~ 1)
```

### block x group

```{r}
study1_block_SL_anova <- anova_test(data = study1_SL_long_block, wid = "Subject", dv = "SL_score", between = "Group", within = "Block", effect.size = "pes")

# greenhouse-geisser correction
get_anova_table(study1_block_SL_anova, correction = c("GG"))
```

### chi-square test

```{r}
study1_SL_offline_table = table(study1_SL$Group, study1_SL$is_learn_offline)
study1_SL_offline_table
chisq.test(study1_SL_offline_table, correct = FALSE)
```

## visuomotor performance
### group

```{r}
# normality test
shapiro_test(study1_VP_long$VP_score)
# homogeneity of variance test
var.test(VP_score ~ Group, data = study1_VP_long)
```

```{r}
study1_VP_anova <- anova_test(data = study1_VP_long, wid = "Subject", dv = "VP_score", between = "Group", effect.size = "pes")

get_anova_table(study1_VP_anova)
```

```{r}
# whole offline
mean(study1_VP_long$VP_score)
sd(study1_VP_long$VP_score)

# normality test
shapiro_test(study1_VP_long$VP_score)

# t-test
t.test(study1_VP_long$VP_score)
cohens_d(study1_VP_long, VP_score ~ 1)
```

```{r}
# lowerAQ group offline
lowerAQ_offline <- study1_VP_long %>% 
  filter(Group == 0)
mean(lowerAQ_offline$VP_score)
sd(lowerAQ_offline$VP_score)

# normality test
shapiro_test(lowerAQ_offline$VP_score)

# t-test
t.test(lowerAQ_offline$VP_score)
cohens_d(lowerAQ_offline, VP_score ~ 1)
```

```{r}
# higherAQ group offline
higherAQ_offline <- study1_VP_long %>% 
  filter(Group == 1)
mean(higherAQ_offline$VP_score)
sd(higherAQ_offline$VP_score)

# normality test
shapiro_test(higherAQ_offline$VP_score)

# t-test
t.test(higherAQ_offline$VP_score)
cohens_d(higherAQ_offline, VP_score ~ 1)
```

### block x group

```{r}
study1_block_VP_anova <- anova_test(data = study1_VP_long_block, wid = "Subject", dv = "VP_score", between = "Group", within = "Block", effect.size = "pes")

# greenhouse-geisser correction
get_anova_table(study1_block_VP_anova, correction = c("GG"))
```

### chi-square test

```{r}
study1_VP_offline_table = table(study1_VP$Group, study1_VP$is_learn_offline)
study1_VP_offline_table
chisq.test(study1_VP_offline_table, correct = FALSE)
```

