---
title: "bayesian_statistics"
author: "Cintia Anna Nagy"
date: "`r Sys.Date()`"
output: html_document
---

# import packages

```{r message = FALSE}
library(tidyverse)
library(car)
library(BayesFactor)
library(bayestestR)
```

# import data

```{r message = FALSE}
study1_SL <- read_csv("processed_data/study_1/data_study_1_SL_offline_online.csv")
study1_VP <- read_csv("processed_data/study_1/data_study_1_VP_offline_online.csv")
study1_stat_learn <- read_csv("processed_data/study_1/data_study_1_statistical_learning.csv")
study1_visuomotor_perf <- read_csv("processed_data/study_1/data_study_1_visuomotor_performance.csv")
study2_SL <- read_csv("processed_data/study_2/data_study_2_SL_offline_online.csv")
study2_VP <- read_csv("processed_data/study_2/data_study_2_VP_offline_online.csv")
study2_stat_learn <- read_csv("processed_data/study_2/data_study_2_statistical_learning.csv")
study2_visuomotor_perf <- read_csv("processed_data/study_2/data_study_2_visuomotor_performance.csv")
```

# preprocess data
## Study 1

```{r}
# make long dataset
study1_SL_long <- study1_SL %>% 
  select(c('Group', 'AQ_total', 'Subject', 'offline_SL'))

learning_phase <- c('offline_SL')

study1_SL_long <- pivot_longer(
  data = study1_SL_long,
  cols = learning_phase,
  names_to = c("Learning_phase"),
  values_to = "SL_score"
)

study1_SL_long <- study1_SL_long %>% 
  mutate(AQ_total_centered = scale(AQ_total, center = T, scale = F))

study1_SL_long <- study1_SL_long %>% 
  drop_na()
```

```{r}
# make long dataset
study1_VP_long <- study1_VP %>% 
  select(c('Group', 'AQ_total', 'Subject', 'offline_VP'))

learning_phase <- c('offline_VP')

study1_VP_long <- pivot_longer(
  data = study1_VP_long,
  cols = learning_phase,
  names_to = c("Learning_phase"),
  values_to = "VP_score"
)

study1_VP_long <- study1_VP_long %>% 
  mutate(AQ_total_centered = scale(AQ_total, center = T, scale = F))

study1_VP_long <- study1_VP_long %>% 
  drop_na()
```

```{r}
# make long dataset
study1_SL_long_block <- study1_SL %>% 
  select(c('Group', 'AQ_total', 'Subject', 'block2_offline','block3_offline', 'block4_offline','block5_offline', 'block6_offline','block7_offline', 'block8_offline','block9_offline', 'block10_offline',
                                       'block11_offline', 'block12_offline','block13_offline', 'block14_offline','block15_offline', 'block16_offline', 'block17_offline','block18_offline', 'block19_offline','block20_offline', 'block21_offline', 'block22_offline','block23_offline', 'block24_offline','block25_offline'))

blocks <- c('block2','block3', 'block4','block5', 'block6','block7', 'block8','block9', 'block10',
               'block11', 'block12','block13', 'block14','block15', 'block16', 'block17','block18',
               'block19','block20', 'block21', 'block22','block23', 'block24','block25')

study1_SL_long_block <- pivot_longer(
  data = study1_SL_long_block,
  cols = starts_with(blocks),
  names_to = c("Block"),
  values_to = "SL_score"
)

study1_SL_long_block <- study1_SL_long_block %>% 
  mutate(Block = gsub('_offline', "", Block)) %>% 
  mutate(Block = gsub('block', "", Block))

study1_SL_long_block <- study1_SL_long_block %>% 
  mutate(Block = as.numeric(Block),
         Block_centered = scale(Block, center = T, scale = F),
         AQ_total_centered = scale(AQ_total, center = T, scale = F))

study1_SL_long_block <- study1_SL_long_block %>% 
  drop_na()
```

```{r}
# make long dataset
study1_VP_long_block <- study1_VP %>% 
  select(c('Group', 'AQ_total', 'Subject', 'block2_offline','block3_offline', 'block4_offline','block5_offline', 'block6_offline','block7_offline', 'block8_offline','block9_offline', 'block10_offline',
                                       'block11_offline', 'block12_offline','block13_offline', 'block14_offline','block15_offline', 'block16_offline', 'block17_offline','block18_offline', 'block19_offline','block20_offline', 'block21_offline', 'block22_offline','block23_offline', 'block24_offline','block25_offline'))

blocks <- c('block2','block3', 'block4','block5', 'block6','block7', 'block8','block9', 'block10',
               'block11', 'block12','block13', 'block14','block15', 'block16', 'block17','block18',
               'block19','block20', 'block21', 'block22','block23', 'block24','block25')

study1_VP_long_block <- pivot_longer(
  data = study1_VP_long_block,
  cols = starts_with(blocks),
  names_to = c("Block"),
  values_to = "VP_score"
)

study1_VP_long_block <- study1_VP_long_block %>% 
  mutate(Block = gsub('_offline', "", Block)) %>% 
  mutate(Block = gsub('block', "", Block))

study1_VP_long_block <- study1_VP_long_block %>% 
  mutate(Block = as.numeric(Block),
         Block_centered = scale(Block, center = T, scale = F),
         AQ_total_centered = scale(AQ_total, center = T, scale = F))

study1_VP_long_block <- study1_VP_long_block %>% 
  drop_na()
```

```{r}
study1_stat_learn_long <- study1_stat_learn %>% 
  select(c('Group', 'Subject', 'e1_H','e2_H','e3_H','e4_H', 'e5_H', 'e1_L','e2_L','e3_L','e4_L', 'e5_L'))

blocks <- c('e1','e2','e3','e4', 'e5')

study1_stat_learn_long <- pivot_longer(
  data = study1_stat_learn_long,
  cols = starts_with(blocks),
  names_to = c(".value", "Triplet"),
  names_pattern = "([^_]+)_(\\D+)",
  values_to = "Triplet"
)

study1_stat_learn_long <- pivot_longer(
  data = study1_stat_learn_long,
  cols = starts_with(blocks),
  names_to = c("Blocks"),
  values_to = "stat_learn"
)

study1_stat_learn_long <- study1_stat_learn_long %>% 
  mutate(Block = gsub('e', "", Blocks))

study1_stat_learn_long <- study1_stat_learn_long %>% 
  drop_na()
```

```{r}
study1_visuomotor_perf_long <- study1_visuomotor_perf %>% 
  select(c('Group', 'Subject', 'e1','e2','e3','e4', 'e5'))

blocks <- c('e1','e2','e3','e4')

study1_visuomotor_perf_long <- pivot_longer(
  data = study1_visuomotor_perf_long,
  cols = starts_with(blocks),
  names_to = c("Blocks"),
  values_to = "visuomotor_perf"
)

study1_visuomotor_perf_long <- study1_visuomotor_perf_long %>% 
  mutate(Block = gsub('e', "", Blocks))

study1_visuomotor_perf_long <- study1_visuomotor_perf_long %>% 
  drop_na()
```

## Study 2

```{r}
# make long dataset
study2_SL_long <- study2_SL %>% 
  select(c('Group', 'Subject', 'offline_SL'))

learning_phase <- c('offline_SL')

study2_SL_long <- pivot_longer(
  data = study2_SL_long,
  cols = learning_phase,
  names_to = c("Learning_phase"),
  values_to = "SL_score"
)

study2_SL_long <- study2_SL_long %>% 
  drop_na()
```

```{r}
# make long dataset
study2_VP_long <- study2_VP %>% 
  select(c('Group', 'Subject', 'offline_VP'))

learning_phase <- c('offline_VP')

study2_VP_long <- pivot_longer(
  data = study2_VP_long,
  cols = learning_phase,
  names_to = c("Learning_phase"),
  values_to = "VP_score"
)

study2_VP_long <- study2_VP_long %>% 
  drop_na()
```

```{r}
# make long dataset
study2_SL_long_block <- study2_SL %>% 
  select(c('Group', 'Subject', 'block2_offline','block3_offline', 'block4_offline','block5_offline', 'block6_offline','block7_offline', 'block8_offline','block9_offline', 'block10_offline',
                                       'block11_offline', 'block12_offline','block13_offline', 'block14_offline','block15_offline', 'block16_offline', 'block17_offline','block18_offline', 'block19_offline','block20_offline'))

blocks <- c('block2','block3', 'block4','block5', 'block6','block7', 'block8','block9', 'block10',
               'block11', 'block12','block13', 'block14','block15', 'block16', 'block17','block18',
               'block19','block20')

study2_SL_long_block <- pivot_longer(
  data = study2_SL_long_block,
  cols = starts_with(blocks),
  names_to = c("Block"),
  values_to = "SL_score"
)

study2_SL_long_block <- study2_SL_long_block %>% 
    mutate(Block = gsub('_offline', "", Block)) %>% 
    mutate(Block = gsub('block', "", Block))

study2_SL_long_block <- study2_SL_long_block %>% 
  drop_na()
```

```{r}
# make long dataset
study2_VP_long_block <- study2_VP %>% 
  select(c('Group', 'Subject', 'block2_offline','block3_offline', 'block4_offline','block5_offline', 'block6_offline','block7_offline', 'block8_offline','block9_offline', 'block10_offline',
                                       'block11_offline', 'block12_offline','block13_offline', 'block14_offline','block15_offline', 'block16_offline', 'block17_offline','block18_offline', 'block19_offline','block20_offline'))

blocks <- c('block2','block3', 'block4','block5', 'block6','block7', 'block8','block9', 'block10',
               'block11', 'block12','block13', 'block14','block15', 'block16', 'block17','block18',
               'block19','block20')

study2_VP_long_block <- pivot_longer(
  data = study2_VP_long_block,
  cols = starts_with(blocks),
  names_to = c("Block"),
  values_to = "VP_score"
)

study2_VP_long_block <- study2_VP_long_block %>% 
  mutate(Block = gsub('_offline', "", Block)) %>% 
  mutate(Block = gsub('block', "", Block))

study2_VP_long_block <- study2_VP_long_block %>% 
  drop_na()
```

```{r}
study2_stat_learn_long <- study2_stat_learn %>% 
  select(c('Group', 'Subject', 'e1_H','e2_H','e3_H','e4_H', 'e1_L','e2_L','e3_L','e4_L'))

blocks <- c('e1','e2','e3','e4')

study2_stat_learn_long <- pivot_longer(
  data = study2_stat_learn_long,
  cols = starts_with(blocks),
  names_to = c(".value", "Triplet"),
  names_pattern = "([^_]+)_(\\D+)",
  values_to = "Triplet"
)

study2_stat_learn_long <- pivot_longer(
  data = study2_stat_learn_long,
  cols = starts_with(blocks),
  names_to = c("Blocks"),
  values_to = "stat_learn"
)

study2_stat_learn_long <- study2_stat_learn_long %>% 
  mutate(Block = gsub('e', "", Blocks))

study2_stat_learn_long <- study2_stat_learn_long %>% 
  drop_na()
```

```{r}
study2_visuomotor_perf_long <- study2_visuomotor_perf %>% 
  select(c('Group', 'Subject', 'e1','e2','e3','e4'))

blocks <- c('e1','e2','e3','e4')

study2_visuomotor_perf_long <- pivot_longer(
  data = study2_visuomotor_perf_long,
  cols = starts_with(blocks),
  names_to = c("Blocks"),
  values_to = "visuomotor_perf"
)

study2_visuomotor_perf_long <- study2_visuomotor_perf_long %>% 
  mutate(Block = gsub('e', "", Blocks))

study2_visuomotor_perf_long <- study2_visuomotor_perf_long %>% 
  drop_na()
```

# Study 1 (AQ)
## statistical learning
### AQ

```{r}
study1_bayes_SL <- extractBF(generalTestBF(SL_score ~ AQ_total, data = study1_SL_long))$bf

1/as.numeric(study1_bayes_SL)
```
### block x group

```{r}
study1_bayes_block_SL <- generalTestBF(SL_score ~ Block*AQ_total,
data = study1_SL_long_block)
```

```{r}
extractBF(study1_bayes_block_SL)
```

```{r}
study1_BF_incl_block_SL <- bayesfactor_inclusion(study1_bayes_block_SL, match_models = TRUE)
study1_BF_incl_block_SL
```

```{r}
# BF_exclusion
1/as.numeric(study1_BF_incl_block_SL)
```

## visuomotor learning
### AQ

```{r}
study1_bayes_VP <- extractBF(generalTestBF(VP_score ~ AQ_total, data = study1_VP_long))$bf

1/as.numeric(study1_bayes_VP)
```
### block x group

```{r}
study1_bayes_block_VP <- generalTestBF(VP_score ~ Block*AQ_total,
data = study1_VP_long_block)
```

```{r}
extractBF(study1_bayes_block_VP)
```

```{r}
study1_BF_incl_block_VP <- bayesfactor_inclusion(study1_bayes_block_VP, match_models = TRUE)
study1_BF_incl_block_VP
```

```{r}
# BF_exclusion
1/as.numeric(study1_BF_incl_block_VP)
```

# Study 1 (group)
## statistical learning 
### group

```{r}
study1_bayes_SL <- extractBF(ttestBF(study1_SL_long$SL_score[study1_SL_long$Group == 0], study1_SL_long$SL_score[study1_SL_long$Group == 1]))$bf

# BF_exclusion
1/as.numeric(study1_bayes_SL)
```

### learning phase

```{r}
# whole sample offline
study1_BF_whole_off_SL <- extractBF(ttestBF(study1_SL_long$SL_score))$bf

# BF01
1/as.numeric(study1_BF_whole_off_SL)
```


```{r}
# lower AQ group offline
lowerAQ_offline <- study1_SL_long %>% 
  filter(Group == 0)

study1_BF_lowerAQ_off_SL <- extractBF(ttestBF(lowerAQ_offline$SL_score))$bf

# BF01
1/as.numeric(study1_BF_lowerAQ_off_SL)
```

```{r}
# higher AQ group offline
higherAQ_offline <- study1_SL_long %>% 
  filter(Group == 1)

study1_BF_higherAQ_off_SL <- extractBF(ttestBF(higherAQ_offline$SL_score))$bf

# BF01
1/as.numeric(study1_BF_higherAQ_off_SL)
```

### block x group

```{r}
study1_bayes_block_SL <- generalTestBF(SL_score ~ Block*Group,
data = study1_SL_long_block)
```

```{r}
extractBF(study1_bayes_block_SL)
```

```{r}
study1_BF_incl_block_SL <- bayesfactor_inclusion(study1_bayes_block_SL, match_models = TRUE)
study1_BF_incl_block_SL
```

```{r}
# BF_exclusion
1/as.numeric(study1_BF_incl_block_SL)
```

## visuomotor performance
### group

```{r}
study1_bayes_VP <- extractBF(ttestBF(study1_VP_long$VP_score[study1_VP_long$Group == 0], study1_VP_long$VP_score[study1_VP_long$Group == 1]))$bf

# BF_exclusion
1/as.numeric(study1_bayes_VP)
```

### learning phase

```{r}
# whole sample offline
study1_BF_whole_off_VP <- extractBF(ttestBF(study1_VP_long$VP_score))$bf

# BF01
1/as.numeric(study1_BF_whole_off_VP)
```


```{r}
# lower AQ group offline
lowerAQ_offline <- study1_VP_long %>% 
  filter(Group == 0)

study1_BF_lowerAQ_off_VP <- extractBF(ttestBF(lowerAQ_offline$VP_score))$bf

# BF01
1/as.numeric(study1_BF_lowerAQ_off_VP)
```

```{r}
# higher AQ group offline
higherAQ_offline <- study1_VP_long %>% 
  filter(Group == 1)

study1_BF_higherAQ_off_VP <- extractBF(ttestBF(higherAQ_offline$VP_score))$bf

# BF01
1/as.numeric(study1_BF_higherAQ_off_VP)
```

### block x group

```{r}
study1_bayes_block_VP <- generalTestBF(VP_score ~ Block*Group,
data = study1_VP_long_block)
```

```{r}
extractBF(study1_bayes_block_VP)
```

```{r}
study1_BF_incl_block_VP <- bayesfactor_inclusion(study1_bayes_block_VP, match_models = TRUE)
study1_BF_incl_block_VP
```

```{r}
# BF_exclusion
1/as.numeric(study1_BF_incl_block_VP)
```

## stat learning

```{r}
bayes_statlearn <- generalTestBF(stat_learn ~ Triplet*Block*Group,
data = study1_stat_learn_long)
```

```{r}
extractBF(bayes_statlearn)
```

```{r}
BF_incl_statlearn <- bayesfactor_inclusion(bayes_statlearn, match_models = TRUE)
BF_incl_statlearn
```

```{r}
# BF_exclusion
1/as.numeric(BF_incl_statlearn)
```

## visuomotor performance

```{r}
bayes_visuomotor_perf <- generalTestBF(visuomotor_perf ~ Block*Group,
data = study1_visuomotor_perf_long)
```

```{r}
extractBF(bayes_visuomotor_perf)
```

```{r}
BF_incl_visuomotor_perf <- bayesfactor_inclusion(bayes_visuomotor_perf, match_models = TRUE)
BF_incl_visuomotor_perf
```

```{r}
# BF_exclusion
1/as.numeric(BF_incl_visuomotor_perf)
```

# Study 2
## statistical learning 
### group

```{r}
study2_bayes_SL <- generalTestBF(SL_score ~ Group, study2_SL_long)
```

```{r}
study2_BF_SL <- extractBF(study2_bayes_SL)$bf
```


```{r}
# BF01
1/as.numeric(study2_BF_SL)
```

### learning phase

```{r}
# whole sample offline
study2_BF_whole_off_SL <- extractBF(ttestBF(study2_SL_long$SL_score))$bf

# BF01
1/as.numeric(study2_BF_whole_off_SL)
```


```{r}
# NTP group offline
NTP_offline <- study2_SL_long %>% 
  filter(Group == 0)

study2_BF_NTP_off_SL <- extractBF(ttestBF(NTP_offline$SL_score))$bf

# BF01
1/as.numeric(study2_BF_NTP_off_SL)
```

```{r}
# higher AQ group offline
ASD_offline <- study2_SL_long %>% 
  filter(Group == 1)

study2_BF_ASD_off_SL <- extractBF(ttestBF(ASD_offline$SL_score))$bf

# BF01
1/as.numeric(study2_BF_ASD_off_SL)
```

### block x group

```{r}
study2_bayes_block_SL <- generalTestBF(SL_score ~ Block*Group,
data = study2_SL_long_block)
```

```{r}
extractBF(study2_bayes_block_SL)
```

```{r}
study2_BF_incl_block_SL <- bayesfactor_inclusion(study2_bayes_block_SL, match_models = TRUE)
study2_BF_incl_block_SL
```

```{r}
# BF_exclusion
1/as.numeric(study2_BF_incl_block_SL)
```

## visuomotor performance
### learning phase x group
### group

```{r}
study2_bayes_VP <- generalTestBF(VP_score ~ Group, study2_VP_long)
```

```{r}
study2_BF_VP <- extractBF(study2_bayes_VP)$bf
```

```{r}
# BF01
1/as.numeric(study2_BF_VP)
```

### learning phase

```{r}
# whole sample offline
study2_BF_whole_off_VP <- extractBF(ttestBF(study2_VP_long$VP_score))$bf

# BF01
1/as.numeric(study2_BF_whole_off_VP)
```


```{r}
# NTP group offline
NTP_offline <- study2_VP_long %>% 
  filter(Group == 0)

study2_BF_NTP_off_VP <- extractBF(ttestBF(NTP_offline$VP_score))$bf

# BF01
1/as.numeric(study2_BF_NTP_off_VP)
```

```{r}
# ASD group offline
ASD_offline <- study2_VP_long %>% 
  filter(Group == 1)

study2_BF_ASD_off_VP <- extractBF(ttestBF(ASD_offline$VP_score))$bf

# BF01
1/as.numeric(study2_BF_ASD_off_VP)
```

### block x group

```{r}
study2_bayes_block_VP <- generalTestBF(VP_score ~ Block*Group,
data = study2_VP_long_block)
```

```{r}
extractBF(study2_bayes_block_VP)
```

```{r}
study2_BF_incl_block_VP <- bayesfactor_inclusion(study2_bayes_block_VP, match_models = TRUE)
study2_BF_incl_block_VP
```

```{r}
# BF_exclusion
1/as.numeric(study2_BF_incl_block_VP)
```

## stat learning

```{r}
bayes_statlearn <- generalTestBF(stat_learn ~ Triplet*Block*Group,
data = study2_stat_learn_long)
```

```{r}
extractBF(bayes_statlearn)
```

```{r}
BF_incl_statlearn <- bayesfactor_inclusion(bayes_statlearn, match_models = TRUE)
BF_incl_statlearn
```

```{r}
# BF_exclusion
1/as.numeric(BF_incl_statlearn)
```

## visuomotor performance

```{r}
bayes_visuomotor_perf <- generalTestBF(visuomotor_perf ~ Block*Group,
data = study2_visuomotor_perf_long)
```

```{r}
extractBF(bayes_visuomotor_perf)
```

```{r}
BF_incl_visuomotor_perf <- bayesfactor_inclusion(bayes_visuomotor_perf, match_models = TRUE)
BF_incl_visuomotor_perf
```

```{r}
# BF_exclusion
1/as.numeric(BF_incl_visuomotor_perf)
```