---
title: "bayesian_statistics"
author: "Cintia Anna Nagy"
date: "`r Sys.Date()`"
output: html_document
---

# import packages

```{r message = FALSE}
library(tidyverse)
library(car)
library(BayesFactor)
library(bayestestR)
```

# import data

```{r message = FALSE}
study1_SL <- read_csv("processed_data/study_1/data_study_1_SL_offline_online.csv")
study1_VP <- read_csv("processed_data/study_1/data_study_1_VP_offline_online.csv")
study2_SL <- read_csv("processed_data/study_2/data_study_2_SL_offline_online.csv")
study2_VP <- read_csv("processed_data/study_2/data_study_2_VP_offline_online.csv")
```

# preprocess data
## Study 1

```{r}
# make long dataset
study1_SL_long <- study1_SL %>% 
  select(c('Group', 'AQ_total', 'Subject', 'online_SL'))

learning_phase <- c('online_SL')

study1_SL_long <- pivot_longer(
  data = study1_SL_long,
  cols = learning_phase,
  names_to = c("Learning_phase"),
  values_to = "SL_score"
)

study1_SL_long <- study1_SL_long %>% 
  mutate(AQ_total_centered = scale(AQ_total, center = T, scale = F))

study1_SL_long <- study1_SL_long %>% 
  drop_na()
```

```{r}
# make long dataset
study1_VP_long <- study1_VP %>% 
  select(c('Group', 'AQ_total', 'Subject', 'online_VP'))

learning_phase <- c('online_VP')

study1_VP_long <- pivot_longer(
  data = study1_VP_long,
  cols = learning_phase,
  names_to = c("Learning_phase"),
  values_to = "VP_score"
)

study1_VP_long <- study1_VP_long %>% 
  mutate(AQ_total_centered = scale(AQ_total, center = T, scale = F))

study1_VP_long <- study1_VP_long %>% 
  drop_na()
```

```{r}
# make long dataset
study1_SL_long_block <- study1_SL %>% 
  select(c('Group', 'AQ_total', 'Subject', 'block2_online','block3_online', 'block4_online','block5_online', 'block6_online','block7_online', 'block8_online','block9_online', 'block10_online',
                                       'block11_online', 'block12_online','block13_online', 'block14_online','block15_online', 'block16_online', 'block17_online','block18_online', 'block19_online','block20_online', 'block21_online', 'block22_online','block23_online', 'block24_online','block25_online'))

blocks <- c('block2','block3', 'block4','block5', 'block6','block7', 'block8','block9', 'block10',
               'block11', 'block12','block13', 'block14','block15', 'block16', 'block17','block18',
               'block19','block20', 'block21', 'block22','block23', 'block24','block25')

study1_SL_long_block <- pivot_longer(
  data = study1_SL_long_block,
  cols = starts_with(blocks),
  names_to = c("Block"),
  values_to = "SL_score"
)

study1_SL_long_block <- study1_SL_long_block %>% 
  mutate(Block = gsub('_online', "", Block)) %>% 
  mutate(Block = gsub('block', "", Block))

study1_SL_long_block <- study1_SL_long_block %>% 
  mutate(Block = as.numeric(Block),
         Block_centered = scale(Block, center = T, scale = F),
         AQ_total_centered = scale(AQ_total, center = T, scale = F))

study1_SL_long_block <- study1_SL_long_block %>% 
  drop_na()
```

```{r}
# make long dataset
study1_VP_long_block <- study1_VP %>% 
  select(c('Group', 'AQ_total', 'Subject', 'block2_online','block3_online', 'block4_online','block5_online', 'block6_online','block7_online', 'block8_online','block9_online', 'block10_online',
                                       'block11_online', 'block12_online','block13_online', 'block14_online','block15_online', 'block16_online', 'block17_online','block18_online', 'block19_online','block20_online', 'block21_online', 'block22_online','block23_online', 'block24_online','block25_online'))

blocks <- c('block2','block3', 'block4','block5', 'block6','block7', 'block8','block9', 'block10',
               'block11', 'block12','block13', 'block14','block15', 'block16', 'block17','block18',
               'block19','block20', 'block21', 'block22','block23', 'block24','block25')

study1_VP_long_block <- pivot_longer(
  data = study1_VP_long_block,
  cols = starts_with(blocks),
  names_to = c("Block"),
  values_to = "VP_score"
)

study1_VP_long_block <- study1_VP_long_block %>% 
  mutate(Block = gsub('_online', "", Block)) %>% 
  mutate(Block = gsub('block', "", Block))

study1_VP_long_block <- study1_VP_long_block %>% 
  mutate(Block = as.numeric(Block),
         Block_centered = scale(Block, center = T, scale = F),
         AQ_total_centered = scale(AQ_total, center = T, scale = F))

study1_VP_long_block <- study1_VP_long_block %>% 
  drop_na()
```

## Study 2

```{r}
# make long dataset
study2_SL_long <- study2_SL %>% 
  select(c('Group', 'Subject', 'online_SL'))

learning_phase <- c('online_SL')

study2_SL_long <- pivot_longer(
  data = study2_SL_long,
  cols = learning_phase,
  names_to = c("Learning_phase"),
  values_to = "SL_score"
)

study2_SL_long <- study2_SL_long %>% 
  drop_na()
```

```{r}
# make long dataset
study2_VP_long <- study2_VP %>% 
  select(c('Group', 'Subject', 'online_VP'))

learning_phase <- c('online_VP')

study2_VP_long <- pivot_longer(
  data = study2_VP_long,
  cols = learning_phase,
  names_to = c("Learning_phase"),
  values_to = "VP_score"
)

study2_VP_long <- study2_VP_long %>% 
  drop_na()
```

```{r}
# make long dataset
study2_SL_long_block <- study2_SL %>% 
  select(c('Group', 'Subject', 'block2_online','block3_online', 'block4_online','block5_online', 'block6_online','block7_online', 'block8_online','block9_online', 'block10_online',
                                       'block11_online', 'block12_online','block13_online', 'block14_online','block15_online', 'block16_online', 'block17_online','block18_online', 'block19_online','block20_online'))

blocks <- c('block2','block3', 'block4','block5', 'block6','block7', 'block8','block9', 'block10',
               'block11', 'block12','block13', 'block14','block15', 'block16', 'block17','block18',
               'block19','block20')

study2_SL_long_block <- pivot_longer(
  data = study2_SL_long_block,
  cols = starts_with(blocks),
  names_to = c("Block"),
  values_to = "SL_score"
)

study2_SL_long_block <- study2_SL_long_block %>% 
    mutate(Block = gsub('_online', "", Block)) %>% 
    mutate(Block = gsub('block', "", Block))

study2_SL_long_block <- study2_SL_long_block %>% 
  drop_na()
```

```{r}
# make long dataset
study2_VP_long_block <- study2_VP %>% 
  select(c('Group', 'Subject', 'block2_online','block3_online', 'block4_online','block5_online', 'block6_online','block7_online', 'block8_online','block9_online', 'block10_online',
                                       'block11_online', 'block12_online','block13_online', 'block14_online','block15_online', 'block16_online', 'block17_online','block18_online', 'block19_online','block20_online'))

blocks <- c('block2','block3', 'block4','block5', 'block6','block7', 'block8','block9', 'block10',
               'block11', 'block12','block13', 'block14','block15', 'block16', 'block17','block18',
               'block19','block20')

study2_VP_long_block <- pivot_longer(
  data = study2_VP_long_block,
  cols = starts_with(blocks),
  names_to = c("Block"),
  values_to = "VP_score"
)

study2_VP_long_block <- study2_VP_long_block %>% 
  mutate(Block = gsub('_online', "", Block)) %>% 
  mutate(Block = gsub('block', "", Block))

study2_VP_long_block <- study2_VP_long_block %>% 
  drop_na()
```

# Study 1 (AQ)
## statistical learning
### AQ

```{r}
study1_bayes_SL <- extractBF(generalTestBF(SL_score ~ AQ_total, data = study1_SL_long))$bf

1/as.numeric(study1_bayes_SL)
```

### block x group

```{r}
study1_bayes_block_SL <- generalTestBF(SL_score ~ Block*AQ_total,
data = study1_SL_long_block)
```

```{r}
extractBF(study1_bayes_block_SL)
```

```{r}
study1_BF_incl_block_SL <- bayesfactor_inclusion(study1_bayes_block_SL, match_models = TRUE)
study1_BF_incl_block_SL
```

```{r}
# BF_exclusion
1/as.numeric(study1_BF_incl_block_SL)
```

## visuomotor learning
### AQ

```{r}
study1_bayes_VP <- extractBF(generalTestBF(VP_score ~ AQ_total, data = study1_VP_long))$bf

1/as.numeric(study1_bayes_VP)
```

### block x group

```{r}
study1_bayes_block_VP <- generalTestBF(VP_score ~ Block*AQ_total,
data = study1_VP_long_block)
```

```{r}
extractBF(study1_bayes_block_VP)
```

```{r}
study1_BF_incl_block_VP <- bayesfactor_inclusion(study1_bayes_block_VP, match_models = TRUE)
study1_BF_incl_block_VP
```

```{r}
# BF_exclusion
1/as.numeric(study1_BF_incl_block_VP)
```

# Study 1 (group)
## statistical learning 
### group

```{r}
study1_bayes_SL <- generalTestBF(SL_score ~ Group, study1_SL_long)
```

```{r}
study1_BF_SL <- extractBF(study1_bayes_SL)$bf
```

```{r}
# BF01
1/as.numeric(study1_BF_SL)
```

### learning phase

```{r}
# whole sample online
study1_BF_whole_off_SL <- extractBF(ttestBF(study1_SL_long$SL_score))$bf

# BF01
1/as.numeric(study1_BF_whole_off_SL)
```


```{r}
# lower AQ group online
lowerAQ_online <- study1_SL_long %>% 
  filter(Group == 0)

study1_BF_lowerAQ_off_SL <- extractBF(ttestBF(lowerAQ_online$SL_score))$bf

# BF01
1/as.numeric(study1_BF_lowerAQ_off_SL)
```

```{r}
# higher AQ group online
higherAQ_online <- study1_SL_long %>% 
  filter(Group == 1)

study1_BF_higherAQ_off_SL <- extractBF(ttestBF(higherAQ_online$SL_score))$bf

# BF01
1/as.numeric(study1_BF_higherAQ_off_SL)
```

### block x group

```{r}
study1_bayes_block_SL <- generalTestBF(SL_score ~ Block*Group,
data = study1_SL_long_block)
```

```{r}
extractBF(study1_bayes_block_SL)
```

```{r}
study1_BF_incl_block_SL <- bayesfactor_inclusion(study1_bayes_block_SL, match_models = TRUE)
study1_BF_incl_block_SL
```

```{r}
# BF_exclusion
1/as.numeric(study1_BF_incl_block_SL)
```

## visuomotor performance
### group

```{r}
study1_bayes_VP <- generalTestBF(VP_score ~ Group, study1_VP_long)
```

```{r}
study1_BF_VP <- extractBF(study1_bayes_VP)$bf
```

```{r}
# BF01
1/as.numeric(study1_BF_VP)
```

### learning phase

```{r}
# whole sample online
study1_BF_whole_off_VP <- extractBF(ttestBF(study1_VP_long$VP_score))$bf

# BF01
1/as.numeric(study1_BF_whole_off_VP)
```


```{r}
# lower AQ group online
lowerAQ_online <- study1_VP_long %>% 
  filter(Group == 0)

study1_BF_lowerAQ_off_VP <- extractBF(ttestBF(lowerAQ_online$VP_score))$bf

# BF01
1/as.numeric(study1_BF_lowerAQ_off_VP)
```

```{r}
# higher AQ group online
higherAQ_online <- study1_VP_long %>% 
  filter(Group == 1)

study1_BF_higherAQ_off_VP <- extractBF(ttestBF(higherAQ_online$VP_score))$bf

# BF01
1/as.numeric(study1_BF_higherAQ_off_VP)
```

### block x group

```{r}
study1_bayes_block_VP <- generalTestBF(VP_score ~ Block*Group,
data = study1_VP_long_block)
```

```{r}
extractBF(study1_bayes_block_VP)
```

```{r}
study1_BF_incl_block_VP <- bayesfactor_inclusion(study1_bayes_block_VP, match_models = TRUE)
study1_BF_incl_block_VP
```

```{r}
# BF_exclusion
1/as.numeric(study1_BF_incl_block_VP)
```

# Study 2
## statistical learning 
### group

```{r}
study2_bayes_SL <- generalTestBF(SL_score ~ Group, study2_SL_long)
```

```{r}
study2_BF_SL <- extractBF(study2_bayes_SL)$bf
```


```{r}
# BF01
1/as.numeric(study2_BF_SL)
```

### learning phase

```{r}
# whole sample online
study2_BF_whole_off_SL <- extractBF(ttestBF(study2_SL_long$SL_score))$bf

# BF01
1/as.numeric(study2_BF_whole_off_SL)
```

```{r}
# NTP group online
NTP_online <- study2_SL_long %>% 
  filter(Group == 0)

study2_BF_NTP_off_SL <- extractBF(ttestBF(NTP_online$SL_score))$bf

# BF01
1/as.numeric(study2_BF_NTP_off_SL)
```

```{r}
# higher AQ group online
ASD_online <- study2_SL_long %>% 
  filter(Group == 1)

study2_BF_ASD_off_SL <- extractBF(ttestBF(ASD_online$SL_score))$bf

# BF01
1/as.numeric(study2_BF_ASD_off_SL)
```

### block x group

```{r}
study2_bayes_block_SL <- generalTestBF(SL_score ~ Block*Group,
data = study2_SL_long_block)
```

```{r}
extractBF(study2_bayes_block_SL)
```

```{r}
study2_BF_incl_block_SL <- bayesfactor_inclusion(study2_bayes_block_SL, match_models = TRUE)
study2_BF_incl_block_SL
```

```{r}
# BF_exclusion
1/as.numeric(study2_BF_incl_block_SL)
```

## visuomotor performance
### learning phase x group
### group

```{r}
study2_bayes_VP <- generalTestBF(VP_score ~ Group, study2_VP_long)
```

```{r}
study2_BF_VP <- extractBF(study2_bayes_VP)$bf
```

```{r}
# BF01
1/as.numeric(study2_BF_VP)
```

### learning phase

```{r}
# whole sample online
study2_BF_whole_off_VP <- extractBF(ttestBF(study2_VP_long$VP_score))$bf

# BF01
1/as.numeric(study2_BF_whole_off_VP)
```

```{r}
# NTP group online
NTP_online <- study2_VP_long %>% 
  filter(Group == 0)

study2_BF_NTP_off_VP <- extractBF(ttestBF(NTP_online$VP_score))$bf

# BF01
1/as.numeric(study2_BF_NTP_off_VP)
```

```{r}
# ASD group online
ASD_online <- study2_VP_long %>% 
  filter(Group == 1)

study2_BF_ASD_off_VP <- extractBF(ttestBF(ASD_online$VP_score))$bf

# BF01
1/as.numeric(study2_BF_ASD_off_VP)
```

### block x group

```{r}
study2_bayes_block_VP <- generalTestBF(VP_score ~ Block*Group,
data = study2_VP_long_block)
```

```{r}
extractBF(study2_bayes_block_VP)
```

```{r}
study2_BF_incl_block_VP <- bayesfactor_inclusion(study2_bayes_block_VP, match_models = TRUE)
study2_BF_incl_block_VP
```

```{r}
# BF_exclusion
1/as.numeric(study2_BF_incl_block_VP)
```
