---
title: "Latent Class Analysis"
author: "Cintia Anna Nagy"
date: "2024-08-18"
output: html_document
---
# import packages

```{r message=FALSE}
library(tidyverse)
library(ggplot2)
library(readxl)
library(psych)
library(plotrix)
library(lcmm)
library(nnet)
library(questionr)
set.seed(500)
```

# import data

```{r message=FALSE}
study1_SL <- read_csv("processed_data/study_1/data_study_1_SL_offline_online.csv")
study1_VP <- read_csv("processed_data/study_1/data_study_1_VP_offline_online.csv")
```

# Staistical learning
## preprocessing

```{r}
study1_SL$ID <- seq.int(nrow(study1_SL))

study1_SL_numeric <- study1_SL %>% 
  select(c('AQ_total', 'block2_offline','block3_offline', 'block4_offline','block5_offline', 'block6_offline','block7_offline', 'block8_offline','block9_offline', 'block10_offline',
                                       'block11_offline', 'block12_offline','block13_offline', 'block14_offline','block15_offline', 'block16_offline', 'block17_offline','block18_offline', 'block19_offline','block20_offline', 'block21_offline', 'block22_offline','block23_offline', 'block24_offline','block25_offline'))

# test normality
sapply(study1_SL_numeric, shapiro.test)

# make long data
study1_SL_long <- study1_SL %>% 
  select(c( 'ID', 'Group', 'AQ_total', 'Subject', 'block2_offline','block3_offline', 'block4_offline','block5_offline', 'block6_offline','block7_offline', 'block8_offline','block9_offline', 'block10_offline',
                                       'block11_offline', 'block12_offline','block13_offline', 'block14_offline','block15_offline', 'block16_offline', 'block17_offline','block18_offline', 'block19_offline','block20_offline', 'block21_offline', 'block22_offline','block23_offline', 'block24_offline','block25_offline'))

blocks <- c('block2','block3', 'block4','block5', 'block6','block7', 'block8','block9', 'block10',
               'block11', 'block12','block13', 'block14','block15', 'block16', 'block17','block18',
               'block19','block20', 'block21', 'block22','block23', 'block24','block25')

study1_SL_long <- pivot_longer(
  data = study1_SL_long,
  cols = starts_with(blocks),
  names_to = c("Block"),
  values_to = "SL_score"
)

study1_SL_long <- study1_SL_long %>% 
  mutate(Block = gsub('_offline', "", Block)) %>% 
  mutate(Block = gsub('block', "", Block))

study1_SL_long <- study1_SL_long %>% 
  mutate(Block = as.numeric(Block)) %>% 
  mutate(Epoch = case_when(
        between(Block, 2, 5)   ~ 1,
        between(Block, 6, 10)  ~ 2,
        between(Block, 11, 15) ~ 3,
        between(Block, 16, 20) ~ 4,
        between(Block, 21, 25) ~ 5
        ))

study1_SL_wide <- study1_SL_long %>% 
  group_by(ID, Subject, Group, AQ_total, Epoch) %>% 
  summarise(SL_score_epoch = median(SL_score, SL_score, na.rm = T)) %>% 
  ungroup()
```

## fit LCA models

```{r}
m1.lin <- hlme(SL_score_epoch ~ Epoch, random = ~Epoch, subject = 'ID', data = study1_SL_wide)
```

```{r}
m2.lin <- gridsearch(hlme(SL_score_epoch ~ Epoch, random = ~Epoch, subject = 'ID', data = study1_SL_wide, ng = 2, mixture = ~Epoch), rep = 200, maxiter = 50, minit = m1.lin)
```

```{r}
m3.lin <- gridsearch(hlme(SL_score_epoch ~ Epoch, random = ~Epoch, subject = 'ID', data = study1_SL_wide, ng = 3, mixture = ~Epoch), rep = 200, maxiter = 50, minit = m1.lin)
```

## compare fit

```{r}
summarytable(m1.lin, m2.lin, m3.lin, which = c("G", "loglik", "conv", "npm", "AIC", "BIC", "SABIC", "entropy", "ICL", "%class"))
```

## summarize model

```{r}
summarytable(m1.lin)

#post.prob <- postprob(m1.lin)
```

## class membership probabilities

```{r}
class.mem <- m1.lin$pprob
logit.class <- car::logit(p = class.mem[ , 3], percents = max(class.mem[ , 3], na.rm = TRUE) > 1)
class.mem.logit.weighted <- cbind(class.mem[ , 1], logit.class)
```

## visualize predicted trajectoires

```{r}
data_pred <- data.frame(Age=c(0,1,4,7))
pred1 <- predictY(m1.lin, data_pred, var.time = "Age", draws =  TRUE)
plot(pred1, lty = 1,  ylab="Learning score (ms)", main="Predicted trajectories for ASRT", xlab = "Age (years)", legend = NULL, shades = TRUE)
legend(x = "topright",legend = c("class1 decrease, N=71",
                             "class2 high start steep decrease, N=3",
                             "class3 increase, N=23"),
       col = c(1,2,3), lwd = c(2), lty = c(1,1), bty = "n", cex = 0.8)

pred2 <- data.frame(pred1[["pred"]])
```

## inspection of residuals

```{r}
plot(m1.lin, cex.main=0.8)
```

## inspection of prosterior probabilities dicstributions

```{r}
plot(m1.lin, which="postprob")
```

## merge with original data

```{r}
regdat <- masterdata[masterdata$Subject %in% class.mem.logit.weighted$Subject,]
regdat <- cbind(regdat,class.mem.logit.weighted[,2:5])
regdat$class <- factor(regdat$class,levels = c(1,2,3),labels = c("decrease","high start steep decrease","increase"))
regdat$high.post.prob<-pmax(regdat$prob1,
                            regdat$prob2,
                            regdat$prob3)

regdat$class2 <- relevel(regdat$class, ref = "decrease")
```

## plot trajectoires in each class

```{r}
regdat$Ypred1 <- ifelse(regdat$class == "decrease",pred2[1,1],
                        ifelse(regdat$class == "increase",pred2[1,3],
                               pred2[1,2]))
regdat$Ypred2 <- ifelse(regdat$class == "decrease",pred2[2,1],
                        ifelse(regdat$class == "increase",pred2[2,3],
                               pred2[2,2]))
regdat$Ypred3 <- ifelse(regdat$class == "decrease",pred2[3,1],
                        ifelse(regdat$class == "increase",pred2[3,3],
                               pred2[3,2]))
regdat$Ypred4 <- ifelse(regdat$class == "decrease",pred2[4,1],
                        ifelse(regdat$class == "increase",pred2[4,3],
                               pred2[4,2]))

plotdat <- gather(regdat,Age,LS,140:143)
plotdat2 <- gather(regdat,Age,Ypred,477:480)
plotdat$Ypred <- plotdat2$Ypred
plotdat$Age <- rep(c(7,8,11,14),each = n)

ggplot(plotdat,aes(Age,Ypred,colour = class,group = Subject)) + 
  geom_line(size = 1.4) +
  geom_point(size = 3.4) +
  geom_line(aes(Age,LS),size = 1.4,alpha = 0.1) +
  geom_point(aes(Age,LS),size = 3.4,alpha = 0.1) +
  theme_classic(base_size = 24) + ylab("Learning score (ms)") + facet_grid(. ~ class) +
  theme(legend.position = "none",strip.background = element_blank()) +
  scale_color_manual(values = c("#4D95B9","#DCC75D","#C35164"))
```

# Visuomotor performance
## preprocessing

```{r}
study1_VP$ID <- seq.int(nrow(study1_VP))

study1_VP_numeric <- study1_VP %>% 
  select(c('AQ_total', 'block2_offline','block3_offline', 'block4_offline','block5_offline', 'block6_offline','block7_offline', 'block8_offline','block9_offline', 'block10_offline',
                                       'block11_offline', 'block12_offline','block13_offline', 'block14_offline','block15_offline', 'block16_offline', 'block17_offline','block18_offline', 'block19_offline','block20_offline', 'block21_offline', 'block22_offline','block23_offline', 'block24_offline','block25_offline'))

# test normality
sapply(study1_VP_numeric, shapiro.test)

# make long data
study1_VP_long <- study1_VP %>% 
  select(c( 'ID', 'Group', 'AQ_total', 'Subject', 'block2_offline','block3_offline', 'block4_offline','block5_offline', 'block6_offline','block7_offline', 'block8_offline','block9_offline', 'block10_offline',
                                       'block11_offline', 'block12_offline','block13_offline', 'block14_offline','block15_offline', 'block16_offline', 'block17_offline','block18_offline', 'block19_offline','block20_offline', 'block21_offline', 'block22_offline','block23_offline', 'block24_offline','block25_offline'))

blocks <- c('block2','block3', 'block4','block5', 'block6','block7', 'block8','block9', 'block10',
               'block11', 'block12','block13', 'block14','block15', 'block16', 'block17','block18',
               'block19','block20', 'block21', 'block22','block23', 'block24','block25')

study1_VP_long <- pivot_longer(
  data = study1_VP_long,
  cols = starts_with(blocks),
  names_to = c("Block"),
  values_to = "VP_score"
)

study1_VP_long <- study1_VP_long %>% 
  mutate(Block = gsub('_offline', "", Block)) %>% 
  mutate(Block = gsub('block', "", Block))

study1_VP_long <- study1_VP_long %>% 
  mutate(Block = as.numeric(Block)) %>% 
  mutate(Epoch = case_when(
        between(Block, 2, 5)   ~ 1,
        between(Block, 6, 10)  ~ 2,
        between(Block, 11, 15) ~ 3,
        between(Block, 16, 20) ~ 4,
        between(Block, 21, 25) ~ 5
        ))

study1_VP_wide <- study1_VP_long %>% 
  group_by(ID, Subject, Group, AQ_total, Epoch) %>% 
  summarise(VP_score_epoch = median(VP_score, VP_score, na.rm = T)) %>% 
  ungroup()
```

## fit LCA models

```{r}
m1.lin <- hlme(VP_score_epoch ~ Epoch, random = ~Epoch, subject = 'ID', data = study1_VP_wide)
```

```{r}
m2.lin <- gridsearch(hlme(VP_score_epoch ~ Epoch, random = ~Epoch, subject = 'ID', data = study1_VP_wide, ng = 2, mixture = ~Epoch), rep = 200, maxiter = 50, minit = m1.lin)
```

```{r}
m3.lin <- gridsearch(hlme(VP_score_epoch ~ Epoch, random = ~Epoch, subject = 'ID', data = study1_VP_wide, ng = 3, mixture = ~Epoch), rep = 200, maxiter = 50, minit = m1.lin)
```

## compare fit

```{r}
summarytable(m1.lin, m2.lin, m3.lin, which = c("G", "loglik", "conv", "npm", "AIC", "BIC", "SABIC", "entropy", "ICL", "%class"))
```

## summarize model

```{r}
summarytable(m1.lin)

#post.prob <- postprob(m1.lin)
```

## class membership probabilities

```{r}
class.mem <- m1.lin$pprob
logit.class <- car::logit(p = class.mem[ , 3], percents = max(class.mem[ , 3], na.rm = TRUE) > 1)
class.mem.logit.weighted <- cbind(class.mem[ , 1], logit.class)
```

## visualize predicted trajectoires

```{r}
data_pred <- data.frame(Age=c(0,1,4,7))
pred1 <- predictY(m1.lin, data_pred, var.time = "Age", draws =  TRUE)
plot(pred1, lty = 1,  ylab="Learning score (ms)", main="Predicted trajectories for ASRT", xlab = "Age (years)", legend = NULL, shades = TRUE)
legend(x = "topright",legend = c("class1 decrease, N=71",
                             "class2 high start steep decrease, N=3",
                             "class3 increase, N=23"),
       col = c(1,2,3), lwd = c(2), lty = c(1,1), bty = "n", cex = 0.8)

pred2 <- data.frame(pred1[["pred"]])
```

## inspection of residuals

```{r}
plot(m1.lin, cex.main=0.8)
```

## inspection of prosterior probabilities dicstributions

```{r}
plot(m1.lin, which="postprob")
```

## merge with original data

```{r}
regdat <- masterdata[masterdata$Subject %in% class.mem.logit.weighted$Subject,]
regdat <- cbind(regdat,class.mem.logit.weighted[,2:5])
regdat$class <- factor(regdat$class,levels = c(1,2,3),labels = c("decrease","high start steep decrease","increase"))
regdat$high.post.prob<-pmax(regdat$prob1,
                            regdat$prob2,
                            regdat$prob3)

regdat$class2 <- relevel(regdat$class, ref = "decrease")
```

## plot trajectoires in each class

```{r}
regdat$Ypred1 <- ifelse(regdat$class == "decrease",pred2[1,1],
                        ifelse(regdat$class == "increase",pred2[1,3],
                               pred2[1,2]))
regdat$Ypred2 <- ifelse(regdat$class == "decrease",pred2[2,1],
                        ifelse(regdat$class == "increase",pred2[2,3],
                               pred2[2,2]))
regdat$Ypred3 <- ifelse(regdat$class == "decrease",pred2[3,1],
                        ifelse(regdat$class == "increase",pred2[3,3],
                               pred2[3,2]))
regdat$Ypred4 <- ifelse(regdat$class == "decrease",pred2[4,1],
                        ifelse(regdat$class == "increase",pred2[4,3],
                               pred2[4,2]))

plotdat <- gather(regdat,Age,LS,140:143)
plotdat2 <- gather(regdat,Age,Ypred,477:480)
plotdat$Ypred <- plotdat2$Ypred
plotdat$Age <- rep(c(7,8,11,14),each = n)

ggplot(plotdat,aes(Age,Ypred,colour = class,group = Subject)) + 
  geom_line(size = 1.4) +
  geom_point(size = 3.4) +
  geom_line(aes(Age,LS),size = 1.4,alpha = 0.1) +
  geom_point(aes(Age,LS),size = 3.4,alpha = 0.1) +
  theme_classic(base_size = 24) + ylab("Learning score (ms)") + facet_grid(. ~ class) +
  theme(legend.position = "none",strip.background = element_blank()) +
  scale_color_manual(values = c("#4D95B9","#DCC75D","#C35164"))
```